---
title: "Alcohol vs Seat choice"
author: "Caina Guardado"
date: "14 September 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$ The is no difference in alcohol consumption based on where on sits in class  
$H_A$ The is a difference in alcohol consumption based on where on sits in class

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
 
  The boxplot shows that the people who sit in the back of the class drink more alcohol than the individual who sit in the front .
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))
```

P value is a small number 0.00016  so we reject the null hypothesis the is no difference in alcohol consumption based on where on sits in class.The turkey model show an internal of zero for middle front  meaning there is no difference in sitting where students sit.

## Conclusions
The drunks hang out in the back row ,unlike the people in the front and middle they consume less alcohol.So we reject the null the hypothesis because there is a difference in sitting and consumption .The p vaule results small whihc will be hard to depilcate the results.

